Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-03-11 paper/ms.tex
started the abstract

\begin{abstract}
-
\end{abstract}

@@

Our observational reference are the recently published results of a
panoramic survey of LAES at z=3.1 by Yamada et al. 2012. This survey
was conducted with the Subaru 8.2m telescope and the Subaru Prime
Focus Camera, which has a field of view covering $34\times 27$ arcmin,
corresponding to a comoving scale of $46\times35$ Mpc $h^{-1}$ at
$z=3.09$. The narrow band filter is centered at $4977$ \AA with a
$77$\AA width, corresponding to the redshift range $z=3.062-3.125$ and
$41$ Mpc $h^{-1}$ comoving scale for the detection of the
Lyman-$\alpha$ line centered at $z=3.09$.

@@

>>>>

\begin{abstract}
In this Letter we implement a new method to find the characteristic
mass of dark matter halos hosting Lyman-Alpha Emitting (LAE)
galaxies. The method is based on matching the statistics for the
cosmic variance with the observations recently obtained by
\cite{Yamada2012}. We build a model for LAEs on top of a large N-body
cosmological simulation (Bolshoi). The basic principle is that a dark
matter halo can host one LAE with a probability $f_{\rm occ}$ if its
mass is found withing a certain range mass range delimited by two
threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
hundreds of mock catalogs in a thourough exploration of the parameter
space of this model. These catalogs are constructed in such a way as
to reproduce the spatial correlation between the different observed
fields. We find that the models that best match the
observed cosmic variance statistics are those with halo masses in the
range $M_{\rm min}=$ and $M_{\rm max}=$ with and occupation fraction
that scales as $f_{\rm occ}=$ with the minimum mass. We find that the
angular correlation function is in agreement with the observational
constraints. 
\end{abstract}

@@

Our observational reference are the recently published results of a
panoramic survey of LAES at z=3.1 by \cite{Yamada2012}. This survey
was conducted with the Subaru 8.2m telescope and the Subaru Prime
Focus Camera, which has a field of view covering $34\times 27$ arcmin,
corresponding to a comoving scale of $46\times35$ Mpc $h^{-1}$ at
$z=3.09$. The narrow band filter is centered at $4977$ \AA with a
$77$\AA width, corresponding to the redshift range $z=3.062-3.125$ and
$41$ Mpc $h^{-1}$ comoving scale for the detection of the
Lyman-$\alpha$ line centered at $z=3.09$.

@@

\section*{Acknowledgments}

\bibliographystyle{mn2e}
\bibliography{references}
